Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Rename TWF-Rec → TWF-ADT for consistency
More consistent \star usage

\begin{figure}[ht]
  \footnotesize
  \drules[TCTX]{$\nonterm G \ctxok$}{context well-formedness}{Empty,Bind}
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr,Rec}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

More formally, we consider the last rule used in the derivation of $\nonterm G \vdash \nonterm{ts}$:
\begin{itemize}
  \item \textsc{TWF-TrueRef}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok}
                  {\nonterm G \vdash \{ v : B | \top \}}
          \longmapsto
        \inferrule{\cdots}
                  {\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok).
    \end{align*}

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Base}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \} \\\\
                   \nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \} \\\\
                   \gterm x \fresh}
                  {\nonterm G \vdash \{ v : B | \nonterm{es}_1 = \nonterm{es}_2 \}}
          \longmapsto
        \inferrule{\Tranterm(\nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \}) \\\\
                   \Tranterm(\nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \}) \\\\
                   \gterm x \fresh \\\\
                   \cdots}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok), \\
                   &\nonterm G ' = \nonterm G , v : \{ v_1 : B | \top \}, \\
                   &\nonterm{ec}_i =
                     \tranterm(\nonterm G ' \vdash \nonterm{es}_i : \{ v_2 : B' | \nonterm{r}_i \}).
    \end{align*}

@@

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
  \item \textsc{TWF-Rec}.
    \todo[inline]{Don't forget to define this.}
\end{itemize}

>>>>

\begin{figure}[ht]
  \footnotesize
  \drules[TCTX]{$\nonterm G \ctxok$}{context well-formedness}{Empty,Bind}
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr,ADT}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

More formally, we consider the last rule used in the derivation of $\nonterm G \vdash \nonterm{ts}$:
\begin{itemize}
  \item \textsc{TWF-TrueRef}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok}
                  {\nonterm G \vdash \{ v : B | \top \}}
          \longmapsto
        \inferrule{\cdots}
                  {\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok).
    \end{align*}

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : \star$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Base}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \} \\\\
                   \nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \} \\\\
                   \gterm x \fresh}
                  {\nonterm G \vdash \{ v : B | \nonterm{es}_1 = \nonterm{es}_2 \}}
          \longmapsto
        \inferrule{\Tranterm(\nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \}) \\\\
                   \Tranterm(\nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \}) \\\\
                   \gterm x \fresh \\\\
                   \cdots}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok), \\
                   &\nonterm G ' = \nonterm G , v : \{ v_1 : B | \top \}, \\
                   &\nonterm{ec}_i =
                     \tranterm(\nonterm G ' \vdash \nonterm{es}_i : \{ v_2 : B' | \nonterm{r}_i \}).
    \end{align*}

@@

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
  \item \textsc{TWF-ADT}.
    \todo[inline]{Don't forget to define this.}
\end{itemize}
